How Residents of Canada Feel about Life and its Correlations with Other Variables in General Social Survey 2017

### 2022-03-21 outputs/paper/paper.Rmd
Preamble

---
title: "My title"
author: 
  - Eunkyo Oh
thanks: "Code and data are available at: https://github.com/oheunkyo/."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

Table of dataset sneak peek

>>>>

---
title: "How Residents of Canada Feel about Life and its Correlations with Other Variables in General Social Survey 2017"
author: 
  - Eunkyo Oh
thanks: "Code and data are available at: https://github.com/oheunkyo/Feelings-on-Life-GSS."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
    includes:  
        in_header: preamble-latex.tex 
        # https://stackoverflow.com/questions/16626462/figure-position-in-markdown-when-converting-to-pdf-with-knitr-and-pandoc/33801326#33801326
toc: FALSE
bibliography: references.bib
---

@@

Table \@ref(tab:dataextract) represents the first ten rows of our dataset. The table was created with `knitr::kable()` [@citeknitr].
